---
title: "Lab Notebook 2024"
author: "Callum Malcolm"
output:
  pdf_document: default
toc: true
toc_float: true
urlcolor: blue
---

```{r setup, include=FALSE, fig.retina = NULL, dpi = 300}
knitr::opts_chunk$set(echo = TRUE)
library(ggplate)
library(tidyverse)
library(readxl)
library(ggforce)
library(scales)
library(prism)
library(knitr)
library(kableExtra)
library(dplyr)
library(xtable)


knitr::opts_chunk$set(echo = TRUE)
library(ggplate)
library(tidyverse)
library(readxl)
library(ggforce)
library(scales)
library(prism)
library(knitr)
library(kableExtra)
library(dplyr)
library(xtable)
library(formatdown)

# Function to format numbers in scientific notation
format_scientific <- function(x) {
  if (is.numeric(x)) {
    formatted <- formatC(x, format = "e", digits = 2)
    parts <- strsplit(formatted, "e")[[1]]
    coef <- parts[1]
    exponent <- as.integer(parts[2])
    paste0("$", coef, " \\times 10^{", exponent, "}$")
  } else {
    x
  }
}

# Function to apply scientific notation formatting to specified columns
apply_scientific_notation <- function(df, cols) {
  df[cols] <- lapply(df[cols], function(col) {
    sapply(col, format_scientific)
  })
  return(df)
}

```

\newpage

# LN Repository

## Rack 1
- Location: Tank 2, Rack 1, Row H (Bottom)

```{r, echo=FALSE, fig.align='center'}

excel_data <- read_excel("~/Library/CloudStorage/OneDrive-UniversityofCambridge/Lab Notebook/Data/LN_Repository.xlsx", sheet = "Sheet1")

# Convert the last column (assuming it's the 4th column here) to character
#excel_data[, ncol(excel_data)] <- as.character(excel_data[, ncol(excel_data)])

# Display the data as a table
knitr::kable(excel_data)

```

# \textbf January 2024

# \textbf February 2024

# \textbf March 2024

# Monday 24-03-2024

## MR - CD20 Flow EpiDrug Pretreatment
### Protocol
1. 1x10e6 cells from each treatment group were split into 3 wells of a 96-well plate
2. Plate spun at 300xg 5 min and supernatant discarded
3. Cells were resuspnded in FACS Staining buffer
  - 1ul CD20 (BD Cat# 562873) per 250uL
  - 12 uL in 3000uL 
4. Plate inbuated in the dark for 20min at 4C
5. Plate spun at 300xg 5 min and supernatant discarded
6. Samples were resuspended in 400uL PBS and transferred to FACS tubes

### Results
- No clear alteration of CD20 expression due to Epigenetic drug pretreatment

# Tuesday 25-03-2024

## RTX EC50_250324 RBL2 - Seeding
- Seeded an EC50 experiment comparing the effects of RTX on Baseline RBL2 in the presence of 25% NHS 
- Seeded 1 plates with the same RBL2 Baseline population
- Used Rixathon (Catalogue#: )

### Plate seeding protocol:  

  1. Diluted cell suspension to seed 10000 cells/well in 50$\mu$L amounts
  
```{r, echo=FALSE, fig.align='center'}

excel_data <- read_excel("~/Library/CloudStorage/OneDrive-UniversityofCambridge/Lab Notebook/Data/Drug Dilution Tables/250324_DDT_EC50.xlsx", sheet = "Sheet3")

columns_to_format <- c("Cell Line", "Cell Count", "Required Cell total", "CS cells/mL")

excel_data <- apply_scientific_notation(excel_data, columns_to_format)

# Display the data as a table
knitr::kable(excel_data)

```

  2. Made RTX dilutions and added to respective wells in 25$\mu$L    
    - [RTX stock] = 10.3 mg/mL    
    - Drug volumes are added in triplicate  
    - Drug volumes are being added consititute 1/4 of well volume:   
      * [RTX working] needs to be 4x [RTX well]   
    - 6 wells per condition, 25$\mu$L per well ~ minimum of 150$\mu$L per condition needed (recommend 200$\mu$L)
  
```{r, echo=FALSE, fig.align='center'}

excel_data <- read_excel("~/Library/CloudStorage/OneDrive-UniversityofCambridge/Lab Notebook/Data/Drug Dilution Tables/250324_DDT_EC50.xlsx", sheet = "Sheet2")

# Display the data as a table
knitr::kable(excel_data, digits = 1)

```
 
 3. Added HIAS/NHS to indicated wells
  * 25$\mu$L/well
  * Final well volume = 25% Serum (HIAS/NHS)
 4. Plate is incubated for 48 hrs at 37C

  
```{r, echo=FALSE}
df <- read_xlsx("~/Library/CloudStorage/OneDrive-UniversityofCambridge/Lab Notebook/Data/Drug Dilution Tables/250324_DDT_EC50.xlsx", sheet = "Sheet4")
title <- "EC50_250324 CDC Test RBL2"


P1 <- plate_plot(
  data = df,
  position = well,
  value = Condition,
  label = Value,
 label_size = 2,
  plate_size = 96,
  plate_type = "round",
  #colour = "#2E008B",
  title = title
)

print(P1)
```

## RBL2 RTX DP - Dose 1
- Began RTX CDC In Vitro dosing
- Seeded RBL2 into 2x 6 well plates

### Dosing Protocol

1. Count CS and dilute to 2x10^5^ cells in 1 mL
  - If cell count is below either re-culture or add required CS amount, spin down, and resuspend in 1mL
2. Add 1mL of cell suspension containing 2x10^5^ cells to respective wells of 6-well plate
3. Made RTX dilutions and added to respective Rx wells in 500$\mu$L    
    - [RTX stock] = 10.3 mg/mL  
    - Drug volumes are being added consititute 1/4 of well volume:   
      * [RTX working] needs to be 4x [RTX well]   
    - 6 wells per RTX dosing, 500$\mu$L per well ~ minimum of 3000$\mu$L per condition needed (recommend 3500$\mu$L)
    - 1.4 uL RTX stock in 3.5mL media
    - 500$\mu$L media added to Cx wells
 3. Added NHS to all wells
  * 500$\mu$L/well
  * Final well volume = 25% Serum (NHS)
 4. Plates incubated for 24 hrs at 37C

### Plate Layout  


```{r, echo=FALSE}
df <- read_xlsx("~/Library/CloudStorage/OneDrive-UniversityofCambridge/Lab Notebook/Data/Lab Notebook - Table excel files/250325_PM.xlsx", sheet = "Sheet1")
title <- "RBL2 RTX DP1 Control 250325"


P1 <- plate_plot(
  data = df,
  position = well,
  value = Condition,
  label = Value,
 label_size = 2,
  plate_size = 6,
  plate_type = "round",
  colour = "#2E008B",
  title = title
)

print(P1)
```


```{r, echo=FALSE}
df <- read_xlsx("~/Library/CloudStorage/OneDrive-UniversityofCambridge/Lab Notebook/Data/Lab Notebook - Table excel files/250325_PM.xlsx", sheet = "Sheet2")
title <- "RBL2 RTX DP1 RR-RBL2 250325"


P1 <- plate_plot(
  data = df,
  position = well,
  value = Condition,
  label = Value,
 label_size = 2,
  plate_size = 6,
  plate_type = "round",
  #colour = "#2E008B",
  title = title
)

print(P1)
```


## RBL2 RTX DP - Sample Collection Baseline
### Collection Protocol
1. 1x10^6^ cells added to eppendorf tubes
2. Spun down @ max speed @ 4C
3. Supernatant removed
4. Pellets flash frozen
5. Pellets saved at -80C


# Thursday 27-03-2024

## EC50_250325 Collection - RBL2 RTX CDC Baseline

- Collected plates seeded on 25-03-2025
- EC Plate collection protocol:
  1. Added 20$\mu$L Cell Titre Blue (CTB) to each conditioned well 
    * 20$\mu$L CTB/100$\mu$L of conditioned well recommended by manufacturer
  2. Incubated for 2hr at 37C
  3. Read on plate reader according to Cell Titre Blue Protocol

### Results:
- HIAS impact on RBL2 CDC similar to RAMOS experiments
- NHS impact on RTX CDC is consistent with previous experiments
  * Cell viability was only reduced to 50%
  * Will repeat with higher doses of RTX (100ug/ml) and more careful cell counting
```{r, echo=FALSE, out.width ='70%', fig.align='center'}

# Path to your image file
image_path <- "~/Library/CloudStorage/OneDrive-UniversityofCambridge/Lab Notebook/Data/Results/250325_EC50_RTX_CDC_RBL2_Baseline1.png"

# Insert the image
knitr::include_graphics(image_path)

``` 

## RBL2 RTX DP - Dose 1 Collection

### Collection Protocol

1. Well volume transferred to 15ml Eppendorf
2. Eppendorfs supn down at 200 rcf for 6 min
3. Supernatant discarded and resuspended in 2ml
4. Collected cells added to individual wells of 6-well plates

# Friday 28-03-2024

## RAMOS-RTXDP SplitSeq: Qubit
- Needed to resumbit library due to low concentration

### SS Qubit Results

```{r, echo=FALSE, fig.align='center'}

excel_data <- read_excel("~/Library/CloudStorage/OneDrive-UniversityofCambridge/Lab Notebook/Data/Library_prep_tables/RTX_DP_SS_QUBIT.xlsx", sheet = "Sheet1")

# Display the data as a table
knitr::kable(excel_data, digits = 1)

```

- CRUK-CI Genomics core tends to ask for 30-40uL of 10-20nM Library Pool

# Monday 31-03-2024

## RAMOS-RTXDP SplitSeq: Library Pooling and Submission
- Library Pooled for submission
- Submission ID: SLX-24264

```{r, echo=FALSE, fig.align='center'}

excel_data <- read_excel("~/Library/CloudStorage/OneDrive-UniversityofCambridge/Lab Notebook/Data/Library_prep_tables/RTX_DP_SS_QUBIT.xlsx", sheet = "Sheet3")

# Display the data as a table
knitr::kable(excel_data, digits = 1)

```

```{r, echo=FALSE, fig.align='center'}

excel_data <- read_excel("~/Library/CloudStorage/OneDrive-UniversityofCambridge/Lab Notebook/Data/Library_prep_tables/RTX_DP_SS_QUBIT.xlsx", sheet = "Sheet4")

# Display the data as a table
knitr::kable(excel_data, digits = 1)

```

## RTX EC50_250331 RBL2 - Seeding
- Seeded an EC50 experiment comparing the effects of RTX on Baseline RBL2 in the presence of 25% NHS 
- Seeded 1 plates with the RBL2 Baseline population
- Used Rixathon (Catalogue#: )

### Plate seeding protocol:  

  1. Diluted cell suspension to seed 10000 cells/well in 50$\mu$L amounts
  
```{r, echo=FALSE, fig.align='center'}

excel_data <- read_excel("~/Library/CloudStorage/OneDrive-UniversityofCambridge/Lab Notebook/Data/Drug Dilution Tables/250331_DDT_EC50.xlsx", sheet = "Sheet3")

columns_to_format <- c("Cell Line", "Cell Count", "Required Cell total", "CS cells/mL")

excel_data <- apply_scientific_notation(excel_data, columns_to_format)

# Display the data as a table
knitr::kable(excel_data)

```

  2. Made RTX dilutions and added to respective wells in 25$\mu$L    
    - [RTX stock] = 10.3 mg/mL    
    - Drug volumes are added in triplicate  
    - Drug volumes are being added consititute 1/4 of well volume:   
      * [RTX working] needs to be 4x [RTX well]   
    - 6 wells per condition, 25$\mu$L per well ~ minimum of 150$\mu$L per condition needed (recommend 200$\mu$L)
  
```{r, echo=FALSE, fig.align='center'}

excel_data <- read_excel("~/Library/CloudStorage/OneDrive-UniversityofCambridge/Lab Notebook/Data/Drug Dilution Tables/250331_DDT_EC50.xlsx", sheet = "Sheet2")

# Display the data as a table
knitr::kable(excel_data, digits = 1)

```
 
 3. Added HIAS/NHS to indicated wells
  * 25$\mu$L/well
  * Final well volume = 25% Serum (HIAS/NHS)
 4. Plate is incubated for 48 hrs at 37C

  
```{r, echo=FALSE}
df <- read_xlsx("~/Library/CloudStorage/OneDrive-UniversityofCambridge/Lab Notebook/Data/Drug Dilution Tables/250331_DDT_EC50.xlsx", sheet = "Sheet4")
title <- "EC50_250331 CDC Test RBL2"


P1 <- plate_plot(
  data = df,
  position = well,
  value = Condition,
  label = Value,
 label_size = 2,
  plate_size = 96,
  plate_type = "round",
  #colour = "#2E008B",
  title = title
)

print(P1)
```


# \textbf April 2025

# Tuesday 01-04-2024

## RTX EC50_250401 RBL2 - Seeding
- Seeded an EC50 experiment comparing the effects of RTX on Baseline RBL2 in the presence of 25% NHS 
- Seeded 1 plates with the RBL2 Baseline population
- Used Rixathon (Catalogue#: )

### Plate seeding protocol:  

  1. Diluted cell suspension to seed 10000 cells/well in 50$\mu$L amounts
  
```{r, echo=FALSE, fig.align='center'}

excel_data <- read_excel("~/Library/CloudStorage/OneDrive-UniversityofCambridge/Lab Notebook/Data/Drug Dilution Tables/250401_DDT_EC50.xlsx", sheet = "Sheet3")

columns_to_format <- c("Cell Line", "Cell Count", "Required Cell total", "CS cells/mL")

excel_data <- apply_scientific_notation(excel_data, columns_to_format)

# Display the data as a table
knitr::kable(excel_data)

```

  2. Made RTX dilutions and added to respective wells in 25$\mu$L    
    - [RTX stock] = 10.3 mg/mL    
    - Drug volumes are added in triplicate  
    - Drug volumes are being added consititute 1/4 of well volume:   
      * [RTX working] needs to be 4x [RTX well]   
    - 6 wells per condition, 25$\mu$L per well ~ minimum of 150$\mu$L per condition needed (recommend 200$\mu$L)
  
```{r, echo=FALSE, fig.align='center'}

excel_data <- read_excel("~/Library/CloudStorage/OneDrive-UniversityofCambridge/Lab Notebook/Data/Drug Dilution Tables/250401_DDT_EC50.xlsx", sheet = "Sheet2")

# Display the data as a table
knitr::kable(excel_data, digits = 1)

```
 
 3. Added HIAS/NHS to indicated wells
  * 25$\mu$L/well
  * Final well volume = 25% Serum (HIAS/NHS)
 4. Plate is incubated for 48 hrs at 37C

  
```{r, echo=FALSE}
df <- read_xlsx("~/Library/CloudStorage/OneDrive-UniversityofCambridge/Lab Notebook/Data/Drug Dilution Tables/250401_DDT_EC50.xlsx", sheet = "Sheet4")
title <- "EC50_250331 CDC Test RBL2"


P1 <- plate_plot(
  data = df,
  position = well,
  value = Condition,
  label = Value,
 label_size = 2,
  plate_size = 96,
  plate_type = "round",
  #colour = "#2E008B",
  title = title
)

print(P1)
```


## RBL2 RTX DP - Dose 1
- Restarted RTX CDC In Vitro dosing
- Concerns with initial seeding/dosing
  * RBL2 appear to be more resistant to RTX dosing
  * Plan is to start with 25ug/mL RTX
  * 25 -> 50 -> 100 -> 200
- Seeded RBL2 into 2x 6 well plates

### Dosing Protocol

1. Count CS and dilute to 5x10^5^ cells in 1 mL
  - If cell count is below either re-culture or add required CS amount, spin down, and resuspend in 1mL
2. Add 1mL of cell suspension containing 5x10^5^ cells to respective wells of 6-well plate
3. Made RTX dilutions and added to respective Rx wells in 500$\mu$L    
    - [RTX stock] = 10.3 mg/mL  
    - Drug volumes are being added consititute 1/4 of well volume:   
      * [RTX working] needs to be 4x [RTX well]   
    - 6 wells per RTX dosing, 500$\mu$L per well ~ minimum of 3000$\mu$L per condition needed (recommend 3500$\mu$L)
    - 25ug/mL [RTX]
      * 34$\mu$L RTX stock in 3.5mL media
      * 100ug/mL WS 
    - 500$\mu$L media added to Cx wells
 3. Added NHS to all wells
  * 500$\mu$L/well
  * Final well volume = 25% Serum (NHS)
 4. Plates incubated for 24 hrs at 37C

### Plate Layout  


```{r, echo=FALSE}
df <- read_xlsx("~/Library/CloudStorage/OneDrive-UniversityofCambridge/Lab Notebook/Data/Lab Notebook - Table excel files/250325_PM.xlsx", sheet = "Sheet1")
title <- "RBL2 RTX DP1 Control 250401"


P1 <- plate_plot(
  data = df,
  position = well,
  value = Condition,
  label = Value,
 label_size = 2,
  plate_size = 6,
  plate_type = "round",
  colour = "#2E008B",
  title = title
)

print(P1)
```


```{r, echo=FALSE}
df <- read_xlsx("~/Library/CloudStorage/OneDrive-UniversityofCambridge/Lab Notebook/Data/Lab Notebook - Table excel files/250325_PM.xlsx", sheet = "Sheet2")
title <- "RBL2 RTX DP1 RR-RBL2 250401"


P1 <- plate_plot(
  data = df,
  position = well,
  value = Condition,
  label = Value,
 label_size = 2,
  plate_size = 6,
  plate_type = "round",
  #colour = "#2E008B",
  title = title
)

print(P1)
```

# Wednesday 02-04-2024

## Media Prep
### Advanced RPMI for PDX
- 20% FBS
#### Recipe

| Solution | ID code | Volume| % Total volume
| :-------: | :------: | :--------:|:----------:|
| Advanced RMPI   | ---- | 500 mL     | 78% |
| Glutamax     | ---- | 6.5 mL    | 20% |
| Pen-Strep    | ---- | 6.5 mL      | 1% |
| FBS     | ---- | 128 mL    | 20% |


## EC50_250331 Collection - RBL2 RTX CDC Baseline

- Collected plates seeded on 25-03-2025
- EC Plate collection protocol:
  1. Added 20$\mu$L Cell Titre Blue (CTB) to each conditioned well 
    * 20$\mu$L CTB/100$\mu$L of conditioned well recommended by manufacturer
  2. Incubated for 2hr at 37C
  3. Read on plate reader according to Cell Titre Blue Protocol

### Results:
- Forgot to seed HIAS
- NHS impact on RTX CDC is consistent with previous experiments
  * Cell viability still wasnt reduced below 50%
  * Will repeat with higher doses of RTX (1000ug/ml) and increased cell/well amount (4x10^5^)
```{r, echo=FALSE, out.width ='70%', fig.align='center'}

# Path to your image file
image_path <- "~/Library/CloudStorage/OneDrive-UniversityofCambridge/Lab Notebook/Data/Results/250331_EC50_RTX_CDC_RBL2_Baseline1.png"

# Insert the image
knitr::include_graphics(image_path)

``` 

## RTX EC50_250402 RBL2 - Seeding
- Seeded an EC50 experiment comparing the effects of RTX on Baseline RBL2 in the presence of 25% NHS 
- Seeded 1 plates with the RBL2 Baseline population
- Used Rixathon (Catalogue#: )

### Plate seeding protocol:  

  1. Diluted cell suspension to seed 40000 cells/well in 50$\mu$L amounts
  
```{r, echo=FALSE, fig.align='center'}

excel_data <- read_excel("~/Library/CloudStorage/OneDrive-UniversityofCambridge/Lab Notebook/Data/Drug Dilution Tables/250401_DDT_EC50.xlsx", sheet = "Sheet3")

columns_to_format <- c("Cell Line", "Cell Count", "Required Cell total", "CS cells/mL")

excel_data <- apply_scientific_notation(excel_data, columns_to_format)

# Display the data as a table
knitr::kable(excel_data)

```

  2. Made RTX dilutions and added to respective wells in 25$\mu$L    
    - [RTX stock] = 10.3 mg/mL    
    - Drug volumes are added in triplicate  
    - Drug volumes are being added consititute 1/4 of well volume:   
      * [RTX working] needs to be 4x [RTX well]   
    - 6 wells per condition, 25$\mu$L per well ~ minimum of 150$\mu$L per condition needed (recommend 200$\mu$L)
  
```{r, echo=FALSE, fig.align='center'}

excel_data <- read_excel("~/Library/CloudStorage/OneDrive-UniversityofCambridge/Lab Notebook/Data/Drug Dilution Tables/250401_DDT_EC50.xlsx", sheet = "Sheet2")

# Display the data as a table
knitr::kable(excel_data, digits = 1)

```
 
 3. Added HIAS/NHS to indicated wells
  * 25$\mu$L/well
  * Final well volume = 25% Serum (HIAS/NHS)
 4. Plate is incubated for 48 hrs at 37C

  
```{r, echo=FALSE}
df <- read_xlsx("~/Library/CloudStorage/OneDrive-UniversityofCambridge/Lab Notebook/Data/Drug Dilution Tables/250401_DDT_EC50.xlsx", sheet = "Sheet4")
title <- "EC50_250331 CDC Test RBL2"


P1 <- plate_plot(
  data = df,
  position = well,
  value = Condition,
  label = Value,
 label_size = 2,
  plate_size = 96,
  plate_type = "round",
  #colour = "#2E008B",
  title = title
)

print(P1)
```

# Thursday 03-04-2024

## RBL2 RTX DP - Dose 1 Collection

### Collection Protocol: RTX Treated

1. Well volume transferred to 15ml Eppendorf
2. Eppendorfs supn down at 200 rcf for 6 min
3. Supernatant discarded and resuspended in 1ml
4. Collected RTX-treated cells added to individual wells of 24-well plates

- Control wells expanded to T25s in 4ml media

## EC50_250401 Collection - RBL2 RTX CDC Baseline

- Collected plates seeded on 25-03-2025
- EC Plate collection protocol:
  1. Added 20$\mu$L Cell Titre Blue (CTB) to each conditioned well 
    * 20$\mu$L CTB/100$\mu$L of conditioned well recommended by manufacturer
  2. Incubated for 2hr at 37C
  3. Read on plate reader according to Cell Titre Blue Protocol

### Results:
- HIAS Results as expected
  * Need to seed one more as reference
- NHS impact on RTX CDC is consistent with previous experiments
  * Cell viability still wasnt reduced below 50%
  * Will repeat with higher doses of RTX (1000ug/ml) and increased cell/well amount (4x10^5^)
```{r, echo=FALSE, out.width ='70%', fig.align='center'}

# Path to your image file
image_path <- "~/Library/CloudStorage/OneDrive-UniversityofCambridge/Lab Notebook/Data/Results/250401_EC50_RTX_CDC_RBL2_Baseline1.png"

# Insert the image
knitr::include_graphics(image_path)

``` 

# Friday 04-04-2024

## EC50_250402 Collection - RBL2 RTX CDC Baseline

- Collected plates seeded on 02-04-2025
- EC Plate collection protocol:
  1. Added 20$\mu$L Cell Titre Blue (CTB) to each conditioned well 
    * 20$\mu$L CTB/100$\mu$L of conditioned well recommended by manufacturer
  2. Incubated for 2hr at 37C
  3. Read on plate reader according to Cell Titre Blue Protocol

### Results:
- NHS impact on RTX CDC is wildly different
  * Down to 30% viability at ~4ug/mL
  * Seems like the issue was cell seeding
  * Will repeat 07-04-2025 with 20ug/mL but 4x10^5^ cells
```{r, echo=FALSE, out.width ='70%', fig.align='center'}

# Path to your image file
image_path <- "~/Library/CloudStorage/OneDrive-UniversityofCambridge/Lab Notebook/Data/Results/250402_EC50_RTX_CDC_RBL2_Baseline1.png"

# Insert the image
knitr::include_graphics(image_path)

``` 











