---
title: "Lab Notebook 2024"
author: "Callum Malcolm"
output:
  pdf_document: default
toc: true
toc_float: true
urlcolor: blue
---

```{r setup, include=FALSE, fig.retina = NULL, dpi = 300}
knitr::opts_chunk$set(echo = TRUE)
library(ggplate)
library(tidyverse)
library(readxl)
library(ggforce)
library(scales)
library(prism)
library(knitr)
library(kableExtra)
library(dplyr)
library(xtable)


knitr::opts_chunk$set(echo = TRUE)
library(ggplate)
library(tidyverse)
library(readxl)
library(ggforce)
library(scales)
library(prism)
library(knitr)
library(kableExtra)
library(dplyr)
library(xtable)
library(formatdown)

# Function to format numbers in scientific notation
format_scientific <- function(x) {
  if (is.numeric(x)) {
    formatted <- formatC(x, format = "e", digits = 2)
    parts <- strsplit(formatted, "e")[[1]]
    coef <- parts[1]
    exponent <- as.integer(parts[2])
    paste0("$", coef, " \\times 10^{", exponent, "}$")
  } else {
    x
  }
}

# Function to apply scientific notation formatting to specified columns
apply_scientific_notation <- function(df, cols) {
  df[cols] <- lapply(df[cols], function(col) {
    sapply(col, format_scientific)
  })
  return(df)
}

```

\newpage

# LN Repository

## Rack 1
- Location: Tank 2, Rack 1, Row H (Bottom)

```{r, echo=FALSE, fig.align='center'}

excel_data <- read_excel("~/Library/CloudStorage/OneDrive-UniversityofCambridge/Lab Notebook/Data/LN_Repository.xlsx", sheet = "Sheet1")

# Convert the last column (assuming it's the 4th column here) to character
#excel_data[, ncol(excel_data)] <- as.character(excel_data[, ncol(excel_data)])

# Display the data as a table
knitr::kable(excel_data)

```

# \textbf January 2024

# \textbf January 2024

# \textbf March 2024

# Monday 24-03-2024

## MR - CD20 Flow EpiDrug Pretreatment
### Protocol
1. 1x10e6 cells from each treatment group were split into 3 wells of a 96-well plate
2. Plate spun at 300xg 5 min and supernatant discarded
3. Cells were resuspnded in FACS Staining buffer
  - 1ul CD20 (BD Cat# 562873) per 250uL
  - 12 uL in 3000uL 
4. Plate inbuated in the dark for 20min at 4C
5. Plate spun at 300xg 5 min and supernatant discarded
6. Samples were resuspended in 400uL PBS and transferred to FACS tubes

### Results
- No clear alteration of CD20 expression due to Epigenetic drug pretreatment

# Tuesday 25-03-2024

## RTX EC50_250324 RBL2 - Seeding
- Seeded an EC50 experiment comparing the effects of RTX on Baseline RBL2 in the presence of 25% NHS 
- Seeded 1 plates with the same RBL2 Baseline population
- Used Rixathon (Catalogue#: )

### Plate seeding protocol:  

  1. Diluted cell suspension to seed 10000 cells/well in 50$\mu$L amounts
  
```{r, echo=FALSE, fig.align='center'}

excel_data <- read_excel("~/Library/CloudStorage/OneDrive-UniversityofCambridge/Lab Notebook/Data/Drug Dilution Tables/250324_DDT_EC50.xlsx", sheet = "Sheet3")

columns_to_format <- c("Cell Line", "Cell Count", "Required Cell total", "CS cells/mL")

excel_data <- apply_scientific_notation(excel_data, columns_to_format)

# Display the data as a table
knitr::kable(excel_data)

```

  2. Made RTX dilutions and added to respective wells in 25$\mu$L    
    - [RTX stock] = 10.3 mg/mL    
    - Drug volumes are added in triplicate  
    - Drug volumes are being added consititute 1/4 of well volume:   
      * [RTX working] needs to be 4x [RTX well]   
    - 6 wells per condition, 25$\mu$L per well ~ minimum of 150$\mu$L per condition needed (recommend 200$\mu$L)
  
```{r, echo=FALSE, fig.align='center'}

excel_data <- read_excel("~/Library/CloudStorage/OneDrive-UniversityofCambridge/Lab Notebook/Data/Drug Dilution Tables/250324_DDT_EC50.xlsx", sheet = "Sheet2")

# Display the data as a table
knitr::kable(excel_data, digits = 1)

```
 
 3. Added HIAS/NHS to indicated wells
  * 25$\mu$L/well
  * Final well volume = 25% Serum (HIAS/NHS)
 4. Plate is incubated for 48 hrs at 37C

  
```{r, echo=FALSE}
df <- read_xlsx("~/Library/CloudStorage/OneDrive-UniversityofCambridge/Lab Notebook/Data/Drug Dilution Tables/250324_DDT_EC50.xlsx", sheet = "Sheet4")
title <- "EC50_250324 CDC Test RBL2"


P1 <- plate_plot(
  data = df,
  position = well,
  value = Condition,
  label = Value,
 label_size = 2,
  plate_size = 96,
  plate_type = "round",
  #colour = "#2E008B",
  title = title
)

print(P1)
```

## RBL2 RTX DP - Dose 1
- Began RTX CDC In Vitro dosing
- Seeded RBL2 into 2x 6 well plates

### Dosing Protocol

1. Count CS and dilute to 2x10^5^ cells in 1 mL
  - If cell count is below either re-culture or add required CS amount, spin down, and resuspend in 1mL
2. Add 1mL of cell suspension containing 2x10^5^ cells to respective wells of 6-well plate
3. Made RTX dilutions and added to respective Rx wells in 500$\mu$L    
    - [RTX stock] = 10.3 mg/mL  
    - Drug volumes are being added consititute 1/4 of well volume:   
      * [RTX working] needs to be 4x [RTX well]   
    - 6 wells per RTX dosing, 500$\mu$L per well ~ minimum of 3000$\mu$L per condition needed (recommend 3500$\mu$L)
    - 1.4 uL RTX stock in 3.5mL media
    - 500$\mu$L media added to Cx wells
 3. Added NHS to all wells
  * 500$\mu$L/well
  * Final well volume = 25% Serum (NHS)
 4. Plates incubated for 24 hrs at 37C

### Plate Layout  


```{r, echo=FALSE}
df <- read_xlsx("~/Library/CloudStorage/OneDrive-UniversityofCambridge/Lab Notebook/Data/Lab Notebook - Table excel files/250325_PM.xlsx", sheet = "Sheet1")
title <- "RBL2 RTX DP1 Control 250325"


P1 <- plate_plot(
  data = df,
  position = well,
  value = Condition,
  label = Value,
 label_size = 2,
  plate_size = 6,
  plate_type = "round",
  colour = "#2E008B",
  title = title
)

print(P1)
```


```{r, echo=FALSE}
df <- read_xlsx("~/Library/CloudStorage/OneDrive-UniversityofCambridge/Lab Notebook/Data/Lab Notebook - Table excel files/250325_PM.xlsx", sheet = "Sheet2")
title <- "RBL2 RTX DP1 RR-RBL2 250325"


P1 <- plate_plot(
  data = df,
  position = well,
  value = Condition,
  label = Value,
 label_size = 2,
  plate_size = 6,
  plate_type = "round",
  #colour = "#2E008B",
  title = title
)

print(P1)
```


## RBL2 RTX DP - Sample Collection Baseline
### Collection Protocol
1. 1x10^6^ cells added to eppendorf tubes
2. Spun down @ max speed @ 4C
3. Supernatant removed
4. Pellets flash frozen
5. Pellets saved at -80C





