---
title: "LNB_Protocol_Templates"
author: "Callum Malcolm"
date: "2024-10-21"
output: pdf_document
---

## EC50 - Seeding
- Explain what was done
- Ex:

- Seeded an EC50 experiment comparing the effects of RTX + 25% NHS vs 25% HIAS on Cx-DP3 cell lines
  * 3x Rx-DP3 lines (R2,R3,R4) exposed to RTX + 25% HIAS
- Seeded 2 plates each section with a different Ramos conditioned lines
  * Plate 1: R2 + R3
  * Plate 2: R4
- Used Rixathon (Catalogue#: )

### Plate seeding protocol:  

  1. Diluted cell suspension to seed 10000 cells/well in 50$\mu$L amounts
  
```{r, echo=FALSE, fig.align='center'}

excel_data <- read_excel("path_to_file", sheet = "Sheet Name")

columns_to_format <- c("Cell Line", "Cell Count", "Required Cell total", "CS cells/mL")

excel_data <- apply_scientific_notation(excel_data, columns_to_format)

# Display the data as a table
knitr::kable(excel_data)

```

  2. Made RTX dilutions and added to respective wells in 25$\mu$L    
    - [RTX stock] = 10.3 mg/mL    
    - Drug volumes are added in triplicate  
    - Drug volumes are being added consititute 1/4 of well volume:   
      * [RTX working] needs to be 4x [RTX well]   
    - 6 wells per condition, 25$\mu$L per well ~ minimum of 150$\mu$L per condition needed (recommend 200$\mu$L)
  
```{r, echo=FALSE, fig.align='center'}

excel_data <- read_excel("path_to_file", sheet = "Sheet Name")

# Display the data as a table
knitr::kable(excel_data, digits = 1)

```
 
 3. Added HIAS/NHS to indicated wells
  * 25$\mu$L/well
  * Final well volume = 25% Serum (HIAS/NHS)
 4. Plate is incubated for 48 hrs at 37C

  
```{r, echo=FALSE}
df <- read_xlsx("path_to_file", sheet = "Sheet Name")
title <- "EC50 240820 Plate 1"


P1 <- plate_plot(
  data = df,
  position = well,
  value = Condition,
  label = Value,
 label_size = 2,
  plate_size = 96,
  plate_type = "round",
  #colour = "#2E008B",
  title = title
)

print(P1)
```

```{r, echo=FALSE}
df <- read_xlsx("path_to_file", sheet = "sheet name")
title <- "Title Name"


P1 <- plate_plot(
  data = df,
  position = well,
  value = Condition,
  label = Value,
 label_size = 2,
  plate_size = 96,
  plate_type = "round",
  #colour = "#2E008B",
  title = title
)

print(P1)
```

## EC50 Collection - Info
- Explain what happened:
- Collected plates seeded on 14-08-2024
- EC Plate collection protocol:
  1. Added 20$\mu$L Cell Titre Blue (CTB) to each conditioned well 
    * 20$\mu$L CTB/100$\mu$L of conditioned well recommended by manufacturer
  2. Incubated for 2hr at 37C
  3. Read on plate reader according to Cell Titre Blue Protocol

### Results:
- HIAS impact on RTX CDC similar to previous experiments
- NHS impact on RTX CDC is consistent with previous experiments
```{r, echo=FALSE, out.width ='70%', fig.align='center'}

# Path to your image file
image_path <- "~/Library/CloudStorage/OneDrive-UniversityofCambridge/Lab Notebook/Data/Results/path_to_file"

# Insert the image
knitr::include_graphics(image_path)

``` 


### Flow Protocol

- Prior to starting: Make cell stain 
  * 500$\mu$L  PBS + 2$\mu$L Stain
  * 100$\mu$L of stain used/condition
- Cell stain made: 2000 $\mu$L and 8 $\mu$L 

1. Resuspend cells and transferred to 3 wells of a 96 well plate
2. Spun down at 1500g for 2min
3. Flick media out
4. Resuspend w/ 100$\mu$L stain in well and consolidate in 1 well
  * Add 100$\mu$L to bottom well and mix until cells resuspended
  * Take 100$\mu$L CS-stain mix and add to well below and mix
  * Repeat for third well and add the total CS-Stain mix to top well
5. Incubate in fridge for 25min
  * In the dark
6. Spin down at 1500g for 2min
7. Flick out media
8. Resuspend in PBS and add to FACS tube
  * Add an additional volume of PBS to dilute cells appropriately for flow
  * Usually make it up to about 300-400$\mu$L CS-PBS in the tube