---
title: "Plate mapping test"
author: "Callum Malcolm"
date: "2024-07-22"
output: pdf_document
---

```{r setup, include=FALSE, fig.retina = NULL, dpi = 300}
knitr::opts_chunk$set(echo = TRUE)
library(ggplate)
library(tidyverse)
library(readxl)

```

# README
Repository for commonly used protocols/code chunks

Add echo=FALSE to hide code, code will not be hidden so it can be copied from PDF

# Protocols

## EC50 Seeding

Ex. ## EC50 RTX N2-BC4/RAMOS-BC5 24401 - Seeding (DNW)
Write an overview of experiment
Ex.
- Seeded an EC50 experiment comparing the effects of RTX on RAMOS-BC5 with or without 10% serum 
- Increased [RTX] to 1mg/mL (closer to Sorcha EC50)
- Used RTX provided by Jamie
- Didn't work because we used Heat Inactivated Serum (HIAS)
- Plate seeding protocol:
  1. Diluted cell suspension to seed 20000 cells/well in 25$\mu$L amounts
  
|Cell Line| Well Number | Required Cell / Volume total | Required cells/mL | Stock cells/mL | **Stock CS Volume** | **Media Volume** |
| :-------: | :------: | :--------:|:----------:|:---------:|:----:|
| RAMOS-BC5| 60 wells | 1.6x10^6^ cells in 2 mL     | 8x10^5^ | 1.6x10^6^ | **1 mL$L** | **1 mL** |

  2. Made RTX dilutions and added to respective wells in 50$\mu$L    
    - [RTX stock] = 10.3 mg/mL   
    - Drug volumes are added in triplicate  
    - Drug volumes are being added consititute 1/4 of well volume: [RTX working] needs to be 4x [RTX well]   
    - 6 wells per condition, 25$\mu$L per well ~ minimum of 150$\mu$L per condition needed (recommend 200$\mu$L)    

  
```{r, echo=FALSE, fig.align='center'}

excel_data <- read_excel("~/Library/CloudStorage/OneDrive-UniversityofCambridge/Lab Notebook/Data/Drug Dilution Tables/240719_DDT.xlsx", sheet = "Sheet3")

columns_to_format <- c("Cell Line", "Cell Count", "Required Cell total", "CS cells/mL")

excel_data <- apply_scientific_notation(excel_data, columns_to_format)

# Display the data as a table
knitr::kable(excel_data)

```
  
  3. Added 10% HIAS or media control
  - This provides complement factors to bind BL-bound RTX and initiate CDC
  - Serum/media amounts added at 50 $\mu$L/well
  - Serum volume is added in 1:4 ratio (10$\mu$L serum in 100$\mu$L final well volume)
  - Serum stock mix is 600$\mu$L HS : 1.2 mL media / plate
  
  4. Plate is incubated for 72 hrs at 37C  


```{r, echo=FALSE}
df <- read_xlsx("~/Library/CloudStorage/OneDrive-UniversityofCambridge/Turner Lab/Write up/Lab Notebook - Table excel files/240322_PM.xlsx", sheet = "Sheet1")
title <- "EC50_RTX_N2-BC4_240401"


P1 <- plate_plot(
  data = df,
  position = well,
  value = Condition,
  label = Value,
 label_size = 2,
  plate_size = 96,
  plate_type = "round",
  #colour = "#2E008B",
  title = title
)

print(P1)
```

## Changing Feeder Cells

Ex. #### Changed FDC:

1. Thawed vial
2. Added 1mL DMEM to vial
3. Transferred to 15mL falcon tube
4. Slowly added 5mL DMEM
5. Spun down at 650rpm for 4min
6. Removed supernant and resuspended vial flicking
7. Added 1mL DMEM and pipetted multiple times to create single cell suspension
8. Added to T175 flask
9. Added 30mL of DMEM
10. Added 5x10^5^ N2 cells from previous flask
10. Placed in incubator

# Code Chunks

## Excel sheets to tables
- For drug dilution tables  
  * Need to make excel file
  * Store in Lab Notebook repository in Data/Drug Dilution Table
  * Reuse templates
  
```{r, echo=FALSE, fig.align='center'}

excel_data <- read_excel("~/Library/CloudStorage/OneDrive-UniversityofCambridge/Lab Notebook/Data/Drug Dilution Tables/240329_DDT.xlsx", sheet = "Sheet1")

# Display the data as a table
knitr::kable(excel_data)

```

# Inserting pictures
- fig.align= (change position)
- out.width= (change size)

```{r, fig.align='center'}

excel_data <- read_excel("~/Library/CloudStorage/OneDrive-UniversityofCambridge/Lab Notebook/Data/Drug Dilution Tables/240430_DDT.xlsx")

# Display the data as a table
knitr::kable(excel_data)

```



## Generating Plate Maps
- Need to make reference excel sheet
- These are stored in Lab Notebook/Data/Lab Notebook - Table excel files


### 6 well Plate
```{r }
df <- read_xlsx("~/Library/CloudStorage/OneDrive-UniversityofCambridge/Turner Lab/Write up/Lab Notebook - Table excel files/241007_PM_1.xlsx", sheet = "Sheet1")


P1 <- plate_plot(
  data = df,
  position = well,
  value = Condition,
  label = Value,
  #label_size = 2,
  plate_size = 6,
  plate_type = "round",
  colour = "#00B6ED"
)

print(P1)
```


### 12 Well Plate
```{r }
df <- read_xlsx("~/Library/CloudStorage/OneDrive-UniversityofCambridge/Turner Lab/Write up/Lab Notebook - Table excel files/241007_PM_1.xlsx", sheet = "Sheet2")
title <- "Plate 2"


P1 <- plate_plot(
  data = df,
  position = well,
  value = Condition,
  label = Value,
 # label_size = 2,
  plate_size = 12,
  plate_type = "round",
  colour = "#2E008B",
  title = title
)

print(P1)
```


### 96 well plate

```{r }
df <- read_xlsx("~/Library/CloudStorage/OneDrive-UniversityofCambridge/Turner Lab/Write up/Lab Notebook - Table excel files/240719_PM.xlsx", sheet = "Sheet1")
title <- "Plate 2"


P1 <- plate_plot(
  data = df,
  position = well,
  value = Condition,
  label = Value,
 label_size = 2,
  plate_size = 96,
  plate_type = "round",
  #colour = "#2E008B",
  title = title
)

print(P1)
```

